Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-05 paper.tex
fixed footnote

To make the print run as close as possible to the actual level of sales, it is 
essential to have an estimation of those sales. 
In this sense, this paper continues our previous work on book sales prediction 
\cite{Castillo2016books} in which the main factors influencing sales where 
analyzed in order to create a tool that the publisher can use to decide how many 
books should be printed.
In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}

>>>>

To make the print run as close as possible to the actual level of sales, it is 
essential to have an estimation of those sales. 
In this sense, this paper continues our previous work on book sales prediction 
\cite{Castillo2016books} in which the main factors influencing sales where 
analyzed in order to create a tool that the publisher can use to decide how many 
books should be printed.
In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{\tt http://editorial.trevenque.es}
